Removal only

### 2020-05-29 analysis/figure-4.Rmd
better suppl file

supplfig4 <- plot_grid(s1a, s1b, s1c, ncol = 1, rel_heights = c(1,1,1.5))
supplfig4

>>>>

contrasts <- png::readPNG("../figures/images/fig_fig4sup1.png")
contrasts <- ggdraw() +  draw_image(contrasts, scale = 1)

supplfig4 <- plot_grid(contrasts, s1a, s1b, s1c, ncol = 1, rel_heights = c(0.5, 1,1,1.5))
supplfig4
